Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline

### 2017-08-07 Ben_Manuscripts/Paper1/results.tex
revisions

@@

We varied the relative interlayer orientation between sandwiched and 
parallel-displaced based on our knowledge of the stability of these two
pi-stacking modes. Short simulations were run with position restraints
on benzene rings. Simulated X-ray diffraction patterns generated from 
each configuration establishes a link between the parallel displaced 
stacking mode and major features present in experimental XRD patterns.  % FIGURE!!!!!!!!!!
The faint ring at a distance of $\approx$ 1.5 \angstrom \textsuperscript{-1} 
is commonly identified as a result of the average packing distance 
between alkane chains. Four spots of higher intensity are visible in the 
alkane chain region creating an x-shaped pattern. The spots are only
generated for structures created in the parallel displaced configuration.
In the past, the spots have been attributed to the tilt angle of the 
alkane chains. Theoretically the angle is the same as that made between 
the spots and the x-axis. However, we achieved the same pattern with 
a calculated average tilt angle of 0 $\pm$ 9 degrees. % GET THE RIGHT NUMBER !!!!!

Further simulation indicates that both configurations are stable for 
100's of nanoseconds. Simulated diffraction of the sandwiched 
configuration after equilibration shows the spots which were not initially
present, implying that there is a shift towards the parallel-displaced
mode. To quantify the degree of sandwiched stacking, we measured the 
amount of overlap between projections of benzene rings and those below
them. The amount of overlap between projections decreases rapidly. % FIGURE !!! overlap

>>>>

% Paragraph describing the experimental 2D WAXS Pattern
The experimental 2D WAXS measurement contains five major reflections which
our model intends to reproduce (Fig ~\ref{fig:WAXSexp}). The first is located
at qz = 1.7 \angstrom \textsuperscript{-1}, corresponding to a real space 
spacing of 3.7 \angstrom. The reflection is attributed to pi-pi stacking
between aromatic rings in the direction perpendicular to the membrane plane, or z-axis. 
For simplicity, this reflection will be referred to as R-pi. A weak intensity
line is located at exactly half the qz value of R-pi (qz = 0.85 \angstrom \textsuperscript{-1}), corresponding to a 
real space periodic spacing of 7.4 \angstroms. This reflection has been 
attributed to 2\textsubscript{1} helical ordering of aromatic rings along the
z axis and will therefore be referred to as R-helix. If positions of the 
aromatic rings can be traced by a helix, then for each turn in the helix, 
there should be two aromatic rings. A third major reflection is marked by 
a low intensity ring located at r = 1.4 \angstrom \textsuperscript{-1}. The
real space separation corresponds to 4.5 \angstroms which is characteristic
of the average spacing between packed alkane chains. This reflection will be
called R-alkanes. Within R-alkanes, are four spots of higher intensity which 
will be called R-spots. All are located \approx 40 degrees from the qz axis
in their respective quadrants. In many liquid crystal systems this can be
attributed to the tilt angle of the alkane chains with respect to the xy axis. 
The final major reflections correspond to the spacing and symmetry of the d100 
plane which can be related to the distance between pores. The feature is
characterized by dots along qz = 0. The spacing between dots is indicative
of the hexagonal symmetry of the packed pores. It is easiest to interpret 
the data by radially integrating the 2D data to get a 1D curve which has
also been done.

@@

We varied the relative interlayer orientation between sandwiched and 
parallel-displaced based on our knowledge of the stability of these two
pi-stacking modes. Short NVT simulations were run with position restraints
on aromatic ring carbon atoms. Simulated X-ray diffraction patterns 
generated from each configuration establish a difference between the two
stacking modes. In each pattern, R-alkanes is present at a distance of
$\approx$ 1.5 \angstrom \textsuperscript{-1}. R-pi is also present in each 
pattern, although it appears to intersect R-alkanes because the spacing
between aromatic rings is similar to the alkane chain packing. The difference 
in aromatic ring spacing between experiment and simulation is likely a result
of the inability of GAFF to properly handle pi interactions. The parallel
displaced configuration contains two lines of high intensity with maximum
intensity occurring where they intersect the alkane chain region due to
constructive interference between the two features. The lines are located
where one would expect to see R-helix. As the simulation is progressed, 
the full line begins to fade and the reflection persists only at the 
intersection with the R-alkanes. Most significantly, the line is no
longer present where R-helix exists and, perhaps coincidentally, the 
intersection with R-alkanes occurs where one would expect to see R-spots.

generated for structures created in the parallel displaced configuration.
In the past, the spots have been attributed to the tilt angle of the 
alkane chains. Theoretically the angle is the same as that made between 
the spots and the x-axis. However, we achieved the same pattern with 
a calculated average tilt angle of 0 $\pm$ 9 degrees. % GET THE RIGHT NUMBER !!!!!

Applying our full equilibration scheme results in structures which indicate
that both configurations are stable for 100's of nanoseconds. Simulated 
diffraction of the sandwiched configuration after equilibration shows the spots which were not initially
present, implying that there is a shift towards the parallel-displaced
mode. To quantify the degree of sandwiched stacking, we measured the 
amount of overlap between projections of benzene rings and those below
them. The amount of overlap between projections decreases rapidly. % FIGURE !!! overlap
